---
title: "State Level Analysis"
date: "4/7/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(kableExtra)
library(zoo)
library(stargazer)
library(sandwich)
library(lmtest)
library(plm)
library(raster)
library(tidyverse)
library(ggplot2)
library(gridExtra)
library(maps)
library(mapproj)
library(lfe)
library(corrplot)
```

```{r, results = F, message = F, warning = F}
setwd('C:/Users/lejac/OneDrive/Documents/Policy-Stats-Team/20_intermediate_data')
final<-read.csv("final_dataset_clean.csv")
```

# Initial Set-Up and (Some) EDA. 

```{r}
#Restrict Year range: 
Rang1 <- seq(2001, 2019, 1)
final <- final %>% filter(year %in% Rang1)

#Generate a new DateTime variable: 
final$Date <- as.Date(final$datetime, "%Y-%m-%d")

#Year to Factor: 
final$year_cat <- as.factor(final$year)

#Convert drug_law to binary factor variable. 
final$drug_law <- as.factor(final$drug_law)

final$scale_tanf_fams <- final$percap_tanf_fams * 100000 # Scale the per capita tanf rate to 100,000 inhabitants

final$scale_num_below_fpl <- final$percap_num_below_fpl * 100000 # Scale the per capita number below the federal poverty to 100,000 inhabitants

#View data: 
kable(head(final))
```

```{r, results = F}
dim(final)
```
### Missing Data. 

```{r, warning = F, message = F, echo = TRUE, comment = ''}
#Missing variables.
#Code is taken from https://jenslaufer.com/data/analysis/visualize_missing_values_with_ggplot.html (for the subsequent three visualizations).  
MISSINGVALS <- final %>%
    gather(key = "key", value = "val") %>%
    mutate(is.missing = is.na(val)) %>%
    group_by(key, is.missing) %>%
    summarise(num.missing = n()) %>%
    filter(is.missing == T) %>%
    dplyr::select(-is.missing) %>%
    arrange(desc(num.missing))

MISSINGVALS
```

```{r}
#Drop NA values: 
final <- final %>% drop_na()

#Identify DC as an outlier; drop: 
final <- final %>% filter(state != 'District of Columbia')

#There are some values that are equal to 0; check that these are missing 
#within the raw data and omit (major outliers). 
final <- final %>% filter(tanf_fams != 0)
```

### Distribution of Outcome Variable of Interest: 

```{r}
xfit <- seq(0, max(final$scale_tanf_fams), length = 100) 
yfit <- dnorm(xfit, mean = mean(final$scale_tanf_fams), sd = sd(final$scale_tanf_fams))

MeanTANF <- mean(final$scale_tanf_fams)
SdTANF <- sd(final$scale_tanf_fams)
above <- MeanTANF + SdTANF
below <- MeanTANF - SdTANF

cols <- c("Dev" = "dodgerblue", "Mean" = "darkred", "Normal" = '#364C54')
CountPlot <- ggplot() + geom_histogram(aes(x = final$scale_tanf_fams), fill = "#BCD2CB", binwidth = 20) + geom_line(aes(x = xfit, y = yfit*2000*150, color = 'Normal'), size = 1) + labs(x = 'TANF Familes Per Capita Scaled to 100,000', y = 'Frequency', title = 'Histogram of TANF Families Per Capita \n Scaled to 100,000') + geom_vline(aes(xintercept = MeanTANF, color = 'Mean'), linetype = 'dashed') + geom_vline(aes(xintercept = below, color = 'Dev'), linetype = 'dashed') + geom_vline(xintercept = above, color = 'dodgerblue', linetype = 'dashed') + theme_classic() + theme(plot.title = element_text(hjust = 0.5)) + scale_color_manual(name = "", labels = c('1 St. Deviation', 'Empirical Mean', 'Normal Distr.'), values = cols) + theme(legend.position="bottom")
CountPlot
```

```{r, warning = F, message = F}
EmpPlot <- ggplot(data = final, mapping = aes(x = Date, y = unemp_rate, color = unemp_rate)) + geom_line() + theme_classic() + theme(legend.position = "none") + labs(x = 'Date', y = 'Unemployment Rate', title = 'Unemployment Rate: 2001 - 2019') + theme(plot.title = element_text(hjust = 0.5)) 
EmpPlot

FamPlot <- ggplot(data = final, mapping = aes(x = Date, y = scale_num_below_fpl)) + geom_line(color = 'darkgray') + stat_smooth(method = 'lm', color = '#364C54', size = 2) + theme_classic() + theme(legend.position = "none") + labs(x = 'Date', y = 'Number of Families Below Federal Poverty Level \n Scaled to 100,000', title = 'Number of Families Below Federal Poverty Level \n Scaled to 100,000: 2001 - 2019') + theme(plot.title = element_text(hjust = 0.5)) 
FamPlot
```

```{r, fig.width = 10, warning = F, message = F}
keep <- c('scale_tanf_fams', 'unemp_rate', 'scale_num_below_fpl')
Data3 <- final[keep]
colnames(Data3) <- c('TANF Families', 'Unemp. Rate', 'Families Below FPL')

M <- cor(Data3)
Correlation <- corrplot(M, method="circle", type = 'upper', col=colorRampPalette(c('navy', "lightblue", '#D7E8C4'))(200), addCoef.col = "black", tl.cex = 0.8, tl.col = 'black')
```




# Identification of Policy States. 

```{r}
#Identify states by drug_law variable: 
Policy <- final %>% filter(drug_law == 1)
Policy_States <- unique(Policy$state)

NoPol <- final %>% filter(drug_law == 0)
NoPolicy_States <- unique(NoPol$state)

#Function to clean and capitalize string variables: 
CapStr <- function(y) {
  c <- strsplit(y, " ")[[1]]
  paste(toupper(substring(c, 1,1)), substring(c, 2),
      sep="", collapse=" ")
}

#Read in U.S. state geographic data: 
us_states <- map_data("state")
us_states$region <- sapply(us_states$region, CapStr)

#Identify policy states and save as a variable: 
IndList <- c()
for (i in us_states$region) {
  if (i %in% Policy_States){
    IndList <- c(IndList, 1)
  }
  else {
    IndList <- c(IndList, 0)
  }
}

us_states$drug_law <- as.factor(IndList)

#Colors from Sam! #BCD2CB (blueish) and #364C54 (dark muted green/blue) and #D7E8C4 (green) and dark gray

#Visualize: 
p <- ggplot(data = us_states,
            aes(x = long, y = lat,
                group = group, fill = drug_law)) + geom_polygon(color = "white", size = 0.20, alpha = 0.75) + coord_map() + labs(x = '', y = '', title = 'State Drug Law Enaction') + theme_classic() + theme(plot.title = element_text(hjust = 0.5)) + scale_fill_manual(name = 'Policy Status', labels = c('No', 'Yes'), values = c('#D7E8C4', '#364C54'))
p
```

# State Level Analysis. 

### Case: Tennessee.

Policy Date: 07/2014. 

Control Region: Kentucky, South Carolina. 

```{r}
StatesList <- c('Tennessee', 'Kentucky', 'South Carolina')
TC <- final %>% filter(state %in% StatesList)
```

```{r}
TCTemp <- final %>% filter(state == 'Tennessee')
CList <- c('Kentucky', 'South Carolina')
cols <- c("Tennessee" = '#364C54', "Control Region" = "darkgray")
TCCon <- final %>% filter(state %in% CList)
PlotEmp <- ggplot() + geom_line(data = TCCon, mapping = aes(x = Date, y = unemp_rate, color = 'Control Region')) + geom_line(data = TCTemp, mapping = aes(x = Date, y = unemp_rate, color = 'Tennessee'), size = 1, alpha = 0.8) + theme_classic() + labs(x = 'Date', y = 'State Unemployment Rate', title = 'State Unemployment Rate Trend \n Tennessee and Control States') + theme(plot.title = element_text(hjust = 0.5)) + theme(legend.position="bottom") + scale_color_manual(name = 'State Group', values = cols)  
```

```{r, warning = F, message = F, fig.height = 3, fig.width = 12}
PlotP <- ggplot() + geom_boxplot(data = TC, mapping = aes(y = scale_num_below_fpl, fill = state)) + theme_classic() + scale_fill_brewer(name = 'State', palette="Blues") + labs(y = 'Families Below the Federal Poverty Line \n Per Capita', title = 'Boxplot of Families Below the Federal Poverty Line Per Capita \n by State') + theme(plot.title = element_text(hjust = 0.5)) + theme(legend.position="bottom") 

grid.arrange(PlotEmp, PlotP, ncol = 2, nrow = 1)
```

```{r}
#Visualize TN and Controls geographically: 
Region1Overall <- c('Kentucky', 'South Carolina')

InterList <- c()
for (i in us_states$region) {
  if (i == 'Tennessee') {
    InterList <- c(InterList, 1)
  }
  else if (i %in% Region1Overall) {
    InterList <- c(InterList, 2)
  }
  else {
    InterList <- c(InterList, 3)
  }
}

us_states$TNRegion <- as.factor(InterList) 

pTN <- ggplot(data = us_states,
            aes(x = long, y = lat,
                group = group, fill = TNRegion)) + geom_polygon(color = "white", size = 0.20, alpha = 0.75) + coord_map() + labs(x = '', y = '', title = 'Tennessee and Control States') + theme_classic() + theme(plot.title = element_text(hjust = 0.5)) + scale_fill_manual(name = 'State Group', labels = c('Tennessee', 'Control States', 'Non-Control States'), values = c('#364C54', '#BCD2CB', 'darkgray'))
```

```{r}
R1 <- final %>% filter(state %in% Region1Overall) 

TN <- final %>% filter(state == 'Tennessee') 

#Define pre and post time periods by breakpoint: 
TNPre <- TN %>% filter(Date <= '2014-07-01')
ControlPre <- R1 %>% filter(Date <= '2014-07-01')

TNPost <- TN %>% filter(Date >= '2014-10-01')
ControlPost <- R1 %>% filter(Date >= '2014-10-01')
```

```{r, warning = F, message = F}
#Visualize simple time trend of TANF families. 
cols <- c("Tennessee" = '#364C54', "Control Region" = "#BCD2CB")
RegInit <- ggplot() + geom_line(TNPre, mapping = aes(x = Date, y = scale_tanf_fams, fill = 'Tennessee', group = 1),
  color = "darkgray", size = 0.20, alpha = 0.75, 
  method = "lm") + stat_smooth(TNPre, mapping = aes(x = Date, y = scale_tanf_fams, fill = 'Tennessee', group = 1),
  color = "darkgray", size = 0.20, alpha = 0.75, 
  method = "lm") + stat_smooth(TNPost, mapping = aes(x = Date, y = scale_tanf_fams, fill = 'Tennessee', group = 1),
  color = "darkgray", size = 0.20, alpha = 0.75,   
  method = "lm") + stat_smooth(ControlPre, mapping = aes(x = Date, y = scale_tanf_fams, fill = 'Control Region', group = 1),
  color = "darkgray", size = 0.20,
  method = "lm"
  ) + geom_vline(xintercept = as.Date('2014-07-01'), linetype="dashed", 
                color = "black", size=0.50) + geom_vline(xintercept = as.Date('2014-10-01'), linetype="dashed", 
                color = "black", size=0.50) + stat_smooth(ControlPost, mapping = aes(x = Date, y = scale_tanf_fams, fill = 'Control Region', group = 1),
  color = "darkgray", size = 0.20, 
  method = "lm"
  ) + labs(x = 'Date', y = 'Percent of Families on TANF', title = 'Linear Time Trends for Percent of Families on TANF: \n Tennessee and Control Region') + theme_classic() + theme(plot.title = element_text(hjust = 0.5)) + scale_fill_manual(name="State Group",values=cols)
```

```{r, fig.height = 3, fig.width = 12, warning = F, message = F}
grid.arrange(pTN, RegInit, ncol = 2, nrow = 1)
```

```{r}
#Now, make a new dataframe with all relevant states: 
StatesListTN <- c('Tennessee', 'Kentucky', 'South Carolina')
TNData <- final %>% filter(state %in% StatesListTN)

#Treatment/Control state indicator: 
P <- c()
for (k in TNData$state){
  if (k == 'Tennessee') {
    P <- c(P, 1)
  }
  else {
    P <- c(P, 0)
  }
}

TNData$State_Ind <- as.factor(P)

#Pre Post indicator: 
PList1 <- c()
Enact_Date <- as.Date('2014-07-01')
for (i in TNData$Date){
  if (i > Enact_Date){
    PList1 <- c(PList1, 1)
  }
  else {
    PList1 <- c(PList1, 0)
  }
}

TNData$Post_Ind <- as.factor(PList1)
TNData$state <- as.factor(TNData$state)
```

```{r, comment = ''}
#Fixed Effects DID model: 
TNReg <- felm(scale_tanf_fams ~ drug_law + Post_Ind + scale_num_below_fpl + unemp_rate + drug_law*Post_Ind | year_cat + state, data = TNData)

summary(TNReg)
```
```{r, fig.height = 2.5, fig.width = 10, fig.align = 'center'}
#Model diagnostics plots: 
Fitted <- TNReg$fitted.values[,1]
Res <- TNReg$residuals[,1]
D <- data.frame(Fitted = Fitted, Residuals = Res)

ThisPlot <- ggplot(data = D, mapping = aes(x = Fitted, y = Residuals)) + geom_point(color = '#364C54', alpha = 0.60) + geom_hline(yintercept = 0, color = 'darkred', linetype = 'dashed') + labs(x = 'Fitted', y = 'Residuals', title = 'Residuals vs. Fitted') + theme_classic() + theme(plot.title = element_text(hjust = 0.5))

Res <- as.data.frame(Res)
colnames(Res) <- c('Residual')

QQ2 <- ggplot(Res, aes(sample = Residual)) + stat_qq(color = '#364C54', alpha = 0.60) + stat_qq_line(color = 'darkred') + labs(x = 'Theoretical', y= 'Sample', title = 'Normal Q-Q Plot') + theme_classic() + theme(plot.title = element_text(hjust = 0.5))

grid.arrange(ThisPlot, QQ2, ncol = 2, nrow = 1)
```


### Case: North Carolina.

Policy Date: 07/2013. 

Control Region: Kentucky, South Carolina, Indiana. 

```{r}
StatesList <- c('North Carolina', 'Kentucky', 'South Carolina', 'Indiana')
TC <- final %>% filter(state %in% StatesList)
```

```{r, warning = F, message = F, fig.height = 3, fig.width = 12}
#Comparison of unemployment rate: 
TCNC <- final %>% filter(state == 'North Carolina')
CList <- c('Kentucky', 'South Carolina', 'Indiana')
cols <- c("North Carolina" = '#364C54', "Control Region" = "darkgray")
TCCon <- final %>% filter(state %in% CList)
PlotEmp <- ggplot() + geom_line(data = TCCon, mapping = aes(x = Date, y = unemp_rate, color = 'Control Region')) + geom_line(data = TCNC, mapping = aes(x = Date, y = unemp_rate, color = 'North Carolina'), size = 1, alpha = 0.8) + theme_classic() + labs(x = 'Date', y = 'State Unemployment Rate', title = 'State Unemployment Rate Trend \n North Carolina and Control States') + theme(plot.title = element_text(hjust = 0.5)) + theme(legend.position="bottom") + scale_color_manual(name = 'State Group', values = cols)  

#Comparison of Num below FPL: 
PlotP <- ggplot() + geom_boxplot(data = TC, mapping = aes(y = scale_num_below_fpl, fill = state)) + theme_classic() + scale_fill_brewer(name = 'State', palette="Blues") + labs(y = 'Families Below the Federal Poverty Line \n Per Capita', title = 'Boxplot of Families Below the Federal Poverty Line Per Capita \n by State') + theme(plot.title = element_text(hjust = 0.5)) + theme(legend.position="bottom") 

#Display: 
grid.arrange(PlotEmp, PlotP, ncol = 2, nrow = 1)
```

```{r}
#Identify State and Control States for plot: 
Region1Overall <- c('Kentucky', 'South Carolina', 'Indiana')

InterList <- c()
for (i in us_states$region) {
  if (i == 'North Carolina') {
    InterList <- c(InterList, 1)
  }
  else if (i %in% Region1Overall) {
    InterList <- c(InterList, 2)
  }
  else {
    InterList <- c(InterList, 3)
  }
}

us_states$NCRegion <- as.factor(InterList) 
```

```{r}
#Visualize state and controls geographically: 
p <- ggplot(data = us_states,
            aes(x = long, y = lat,
                group = group, fill = NCRegion)) + geom_polygon(color = "white", size = 0.20, alpha = 0.75) + coord_map() + labs(x = '', y = '', title = 'North Carolina and Control States') + theme_classic() + theme(plot.title = element_text(hjust = 0.5)) + scale_fill_manual(name = 'State Group', labels = c('North Carolina', 'Control States', 'Non-Control States'), values = c('#364C54', '#BCD2CB', 'darkgray'))
```

```{r}
Region1 <- c('Kentucky', 'South Carolina', 'Indiana')

R1 <- final %>% filter(state %in% Region1) 

WV <- final %>% filter(state == 'North Carolina')

#Define Pre and Post data: 

WVPre <- WV %>% filter(Date <= '2013-07-01')
ControlPre <- R1 %>% filter(Date <= '2013-07-01')

WVPost <- WV %>% filter(Date >= '2013-10-01')
ControlPost <- R1 %>% filter(Date >= '2013-10-01')
```


```{r, message = F, warning = F}
cols <- c("North Carolina" = '#364C54', "Control Region" = "#BCD2CB")
RegInit <- ggplot() + stat_smooth(WVPre, mapping = aes(x = Date, y = scale_tanf_fams, fill = 'North Carolina', group = 1),
  color = "darkgray", size = 0.20,
  method = "loess") + stat_smooth(WVPost, mapping = aes(x = Date, y = scale_tanf_fams, fill = 'North Carolina', group = 1),
  color = "darkgray", size = 0.20, 
  method = "loess"
  ) + stat_smooth(ControlPre, mapping = aes(x = Date, y = scale_tanf_fams, fill = 'Control Region', group = 1),
  color = "darkgray", size = 0.20,
  method = "loess"
  ) + geom_vline(xintercept = as.Date('2013-07-01'), linetype="dashed", 
                color = "black", size=0.50) + geom_vline(xintercept = as.Date('2013-10-01'), linetype="dashed", 
                color = "black", size=0.50) + stat_smooth(ControlPost, mapping = aes(x = Date, y = scale_tanf_fams, fill = 'Control Region', group = 1),
  color = "darkgray", size = 0.20, 
  method = "loess"
  ) + labs(x = 'Date', y = 'Percent of Families on TANF', title = 'Linear Time Trends for Percent of Families on TANF: \n North Carolina and Control Region') + theme_classic() + theme(plot.title = element_text(hjust = 0.5)) + scale_fill_manual(name="State Group",values=cols)
```

```{r, fig.height = 3, fig.width = 12, warning = F, message = F}
grid.arrange(p, RegInit, ncol = 2, nrow = 1)
```

```{r}
#State indicator variable: 
PTC <- c()
for (k in TC$state){
  if (k == 'North Carolina') {
    PTC <- c(PTC, 1)
  }
  else {
    PTC <- c(PTC, 0)
  }
}

TC$State_Ind <- as.factor(PTC)

#Pre Post Indicator variable: 
PList <- c()
Enact_Date <- as.Date('2013-07-01')
for (i in TC$Date){
  if (i > Enact_Date){
    PList <- c(PList, 1)
  }
  else {
    PList <- c(PList, 0)
  }
}

TC$Post_Ind <- as.factor(PList)
TC$state <- as.factor(TC$state)
```

```{r, comment = ''}
#Fixed Effects DID model: 
NCReg <- felm(scale_tanf_fams ~ drug_law + Post_Ind + scale_num_below_fpl + unemp_rate + drug_law*Post_Ind | year_cat + state, data = TC)

summary(NCReg)
```
```{r, fig.height = 2.5, fig.width = 10, fig.align = 'center'}
#Model diagnostics: 
Fitted <- NCReg$fitted.values[,1]
Res <- NCReg$residuals[,1]
D <- data.frame(Fitted = Fitted, Residuals = Res)

ThisPlot <- ggplot(data = D, mapping = aes(x = Fitted, y = Residuals)) + geom_point(color = '#364C54', alpha = 0.60) + geom_hline(yintercept = 0, color = 'darkred', linetype = 'dashed') + labs(x = 'Fitted', y = 'Residuals', title = 'Residuals vs. Fitted') + theme_classic() + theme(plot.title = element_text(hjust = 0.5))

Res <- as.data.frame(Res)
colnames(Res) <- c('Residual')

QQ2 <- ggplot(Res, aes(sample = Residual)) + stat_qq(color = '#364C54', alpha = 0.60) + stat_qq_line(color = 'darkred') + labs(x = 'Theoretical', y= 'Sample', title = 'Normal Q-Q Plot') + theme_classic() + theme(plot.title = element_text(hjust = 0.5))

grid.arrange(ThisPlot, QQ2, ncol = 2, nrow = 1)
```

# Case: Alabama.

Policy Date: 04/2014. 

Control Region: Colorado, New Mexico, Ohio. 

```{r}
StatesList <- c('Alabama', 'Colorado', 'New Mexico', 'Ohio')
AL <- final %>% filter(state %in% StatesList)
```

```{r}
TCTemp <- final %>% filter(state == 'Alabama')
CList <- c('Colorado', 'New Mexico', 'Ohio')
cols <- c('Alabama' = '#364C54', "Control Region" = "darkgray")
TCCon <- final %>% filter(state %in% CList)
PlotEmp <- ggplot() + geom_line(data = TCCon, mapping = aes(x = Date, y = unemp_rate, color = 'Control Region')) + geom_line(data = TCTemp, mapping = aes(x = Date, y = unemp_rate, color = 'Alabama'), size = 1, alpha = 0.8) + theme_classic() + labs(x = 'Date', y = 'State Unemployment Rate', title = 'State Unemployment Rate Trend \n Alabama and Control States') + theme(plot.title = element_text(hjust = 0.5)) + theme(legend.position="bottom") + scale_color_manual(name = 'State Group', values = cols)  
```

```{r, warning = F, message = F, fig.height = 3, fig.width = 12}
PlotP <- ggplot() + geom_boxplot(data = AL, mapping = aes(y = scale_num_below_fpl, fill = state)) + theme_classic() + scale_fill_brewer(name = 'State', palette="Blues") + labs(y = 'Families Below the Federal Poverty Line \n Per Capita', title = 'Boxplot of Families Below the Federal Poverty Line Per Capita \n by State') + theme(plot.title = element_text(hjust = 0.5)) + theme(legend.position="bottom") 

grid.arrange(PlotEmp, PlotP, ncol = 2, nrow = 1)
```

```{r}
Region1Overall <- c('Colorado', 'New Mexico', 'Ohio')

InterList <- c()
for (i in us_states$region) {
  if (i == 'Alabama') {
    InterList <- c(InterList, 1)
  }
  else if (i %in% Region1Overall) {
    InterList <- c(InterList, 2)
  }
  else {
    InterList <- c(InterList, 3)
  }
}

us_states$ALRegion <- as.factor(InterList) 
```

```{r}
p <- ggplot(data = us_states,
            aes(x = long, y = lat,
                group = group, fill = ALRegion)) + geom_polygon(color = "white", size = 0.20, alpha = 0.75) + coord_map() + labs(x = '', y = '', title = 'Alabama and Control States') + theme_classic() + theme(plot.title = element_text(hjust = 0.5)) + scale_fill_manual(name = 'State Group', labels = c('Alabama', 'Control States', 'Non-Control States'), values = c('#364C54', '#BCD2CB', 'darkgray'))
```

```{r}
Region1 <- c('Colorado', 'New Mexico', 'Ohio')

R1 <- final %>% filter(state %in% Region1) 

AL <- final %>% filter(state == 'Alabama') 

ALPre <- AL %>% filter(Date <= '2014-04-01')
ControlPre <- R1 %>% filter(Date <= '2014-04-01')

#Define breakpoint. 

ALPost <- AL %>% filter(Date >= '2014-07-01')
ControlPost <- R1 %>% filter(Date >= '2014-07-01')
```

```{r, message = F, warning = F}
cols <- c("Alabama" = '#364C54', "Control Region" = "#BCD2CB")
RegInit <- ggplot() + stat_smooth(ALPre, mapping = aes(x = Date, y = scale_tanf_fams, fill = 'Alabama', group = 1),
  color = "darkgray", size = 0.20,
  method = "loess") + stat_smooth(ALPost, mapping = aes(x = Date, y = scale_tanf_fams, fill = 'Alabama', group = 1),
  color = "darkgray", size = 0.20, 
  method = "loess"
  ) + stat_smooth(ControlPre, mapping = aes(x = Date, y = scale_tanf_fams, fill = 'Control Region', group = 1),
  color = "darkgray", size = 0.20,
  method = "loess"
  ) + geom_vline(xintercept = as.Date('2014-04-01'), linetype="dashed", 
                color = "black", size=0.50) + geom_vline(xintercept = as.Date('2014-07-01'), linetype="dashed", 
                color = "black", size=0.50) + stat_smooth(ControlPost, mapping = aes(x = Date, y = scale_tanf_fams, fill = 'Control Region', group = 1),
  color = "darkgray", size = 0.20, 
  method = "loess"
  ) + labs(x = 'Date', y = 'Percent of Families on TANF', title = 'Linear Time Trends for Percent of Families on TANF: \n Alabama and Control Region') + theme_classic() + theme(plot.title = element_text(hjust = 0.5)) + scale_fill_manual(name="State Group",values=cols)
```

```{r, fig.height = 3, fig.width = 12, warning = F, message = F}
grid.arrange(p, RegInit, ncol = 2, nrow = 1)
```

```{r}
AL <- final %>% filter(state %in% StatesList)
PTC <- c()
for (k in AL$state){
  if (k == 'Alabama') {
    PTC <- c(PTC, 1)
  }
  else {
    PTC <- c(PTC, 0)
  }
}

AL$State_Ind <- as.factor(PTC)

PList <- c()
Enact_Date <- as.Date('2014-04-01')
for (i in AL$Date){
  if (i > Enact_Date){
    PList <- c(PList, 1)
  }
  else {
    PList <- c(PList, 0)
  }
}

AL$Post_Ind <- as.factor(PList)
AL$state <- as.factor(TC$state)
```

```{r, comment = ''}
ALReg <- felm(scale_tanf_fams ~ drug_law + Post_Ind + scale_num_below_fpl + unemp_rate + drug_law*Post_Ind | year_cat + state, data = AL)

summary(ALReg)
```
```{r, fig.height = 2.5, fig.width = 10, fig.align = 'center'}
Fitted <- ALReg$fitted.values[,1]
Res <- ALReg$residuals[,1]
D <- data.frame(Fitted = Fitted, Residuals = Res)

ThisPlot <- ggplot(data = D, mapping = aes(x = Fitted, y = Residuals)) + geom_point(color = '#364C54', alpha = 0.60) + geom_hline(yintercept = 0, color = 'darkred', linetype = 'dashed') + labs(x = 'Fitted', y = 'Residuals', title = 'Residuals vs. Fitted') + theme_classic() + theme(plot.title = element_text(hjust = 0.5))

Res <- as.data.frame(Res)
colnames(Res) <- c('Residual')

QQ2 <- ggplot(Res, aes(sample = Residual)) + stat_qq(color = '#364C54', alpha = 0.60) + stat_qq_line(color = 'darkred') + labs(x = 'Theoretical', y= 'Sample', title = 'Normal Q-Q Plot') + theme_classic() + theme(plot.title = element_text(hjust = 0.5))

grid.arrange(ThisPlot, QQ2, ncol = 2, nrow = 1)
```

# Save

```{r, comment = ''}
print("done")
```

